Discriminative Sensing Based on Signal Processing

### 2017-10-21 docs/thesis/chapters/2_pca_svm_cfa/pca_svm_cfa.tex
minor

@@

In order to audit IT governance of public institutions, the Federal Court of Accounts (TCU, in Portuguese) surveys data of IT practices from these institutions. Although these surveys started in 2007 with 39 questions, nowadays they contain more than 100 questions that allow TCU to rank these institutions by their IT governance index.

@@

To the best of our knowledge, we are the first to propose a critical factors analysis based on PCA for visual discriminative analysis and based on RFE combined with SVM for CSF identification.

@@

Para prever a classificação de uma instituição de acordo com suas respostas para as questões do questionário iGovTI, foram avaliados algoritmos de classificação que pudessem apresentar acurácia para a classificação de organizações de acordo com o iGovTI. Uma vez encontrado um algoritmo capaz desta classificação, é possível utilizar o algoritmo selecionado em conjunto com técnicas de feature selection para identificar as questões mais relevantes para a classificação da instituição de acordo com o iGovTI.
Assim, para a definição do algoritmo de classificação foram realizados testes em 21 algoritmos, a seguir é apresentada uma listagem dos algoritmos avaliados e a taxa de acerto de classificação obtida: 
1. KNN: 0.714286
2. ElasticNet: 0.155336
3. ElasticNetCV: 0.831531
4. LassoCV: 0.827440
5. LassoLarsIC: 0.713763
6. LinearRegression: 0.360878
7. LogisticRegression: 0.771429
8. OrthogonalMatchingPursuit: 0.769630
9. PassiveAggressiveClassifier: 0.800000
10. PassiveAggressiveRegressor: 0.852184
11. Perceptron: 0.800000
12. Ridge: 0.529922
13. RidgeClassifier: 0.657143
14. RidgeClassifierCV: 0.742857
15. RidgeCV: 0.750149
16. SGDClassifier: 0.828571
17. MultinomialNB: 0.742857
18. lda.LDA: 0.628571
19. SVM.SVR: 0.826885
20. SVM.SVC: 0.914286
21. SVM.LinearSVC: 0.714286
22. O algoritmo que obteve maior sucesso para classificação foi o SVC, que é uma implementação de Máquina de Vetores de Suporte aplicado para a classificação. SVC apresentou uma taxa de acerto de 91,4\%. Para a avaliação dos algoritmos, utilizamos uma metodologia que divide os dados dos questionários pelo iGovTI entre questões que serão utilizadas para aprendizado do algoritmo e questões que serão utilizadas para comparativo de predições. Para treinar o algoritmo utilizou-se 90\% dos dados e os 10\% restantes foram utilizados para avaliar a eficiência de classificação dos algoritmos, comparando a taxa de acerto entre as predições feitas e os valores reais de classificações de organizações pelo iGovTI. 
23. Uma vez identificado um algoritmo capaz de efetuar a classificação desejada, o próximo passo é identificar as variáveis mais relevantes para esta classificação. Para isso, será utilizado o algoritmo ERV. 
24. 
4.5 Eliminação Recursiva de Variáveis
25. 
26. A ERV pode usar vários algoritmos de classificação como critério de seleção das variáveis mais importantes, escolhemos o algoritmo SVC por ele ter apresentado maior acurácia entre os algoritmos de classificação avaliados. Ainda é necessário definir o quantitativo de variáveis mais importantes a serem selecionadas. A partir da pesquisa de identificação por meio de entrevistas na APF, identificou-se 54 variáveis consideradas FCS, este critério foi utilizado para determinar o quantitativo de variáveis mais importantes para a classificação.
27. Assim, aplicaram-se o algoritmo ERV utilizando o SVC como critério para a seleção das variáveis mais importantes para a classificação, selecionando as 54 variáveis que correspondem aos FCS levantados nas entrevistas com os executivos de TI. Os resultados mostraram que 69,9\% das variáveis foram classificadas da mesma forma que os FCS identificados anteriormente (Quadro 10) por meio de pesquisa qualitativa.

@@

support vector machines (SVMs) which have been shown to generalize well even for small sample classification[8].

>>>>

To the best of our knowledge, we are the first to propose a critical factors analysis based on PCA for visual discriminative analysis and based on RFE combined with SVM for CSF identification from IT governance data.

@@

The Federal Court of Accounts (TCU, in Portuguese) surveys data of IT practices of brazilian public organizations in order to audit IT governance. This resulting dataset is called iGovTI. We propose to use the iGovTI of 2012 for CSF analysis. The iGovTI is composed by 201 questions used for organization ranking according to their responses and their IT governance.

@@

@@

Para prever a classificação de uma instituição de acordo com suas respostas para as questões do questionário iGovTI, foram avaliados algoritmos de classificação que pudessem apresentar acurácia para a classificação de organizações de acordo com o iGovTI. Uma vez encontrado um algoritmo capaz desta classificação, é possível utilizar o algoritmo selecionado em conjunto com técnicas de feature selection para identificar as questões mais relevantes para a classificação da instituição de acordo com o iGovTI.
Assim, para a definição do algoritmo de classificação foram realizados testes em 21 algoritmos, a seguir é apresentada uma listagem dos algoritmos avaliados e a taxa de acerto de classificação obtida:

k-nearest neighbors \cite{fukunaga1975branch}	0.714286
Elastic Net \cite{zou2005regularization}	0.831531
Lasso \cite{tibshirani1996regression}	0.827440
LinearRegression \cite{draper2014applied}	0.360878
LogisticRegression \cite{hosmer2013applied}	0.771429
LDA \cite{martinez2001pca}	0.628571
SVM \cite{hearst1998support}	0.914286
SVM Regression \cite{smola2004tutorial}	0.826885
Linear SVM \cite{fan2008liblinear}	0.714286

O algoritmo que obteve maior sucesso para classificação foi o SVC, que é uma implementação de Máquina de Vetores de Suporte aplicado para a classificação. SVC apresentou uma taxa de acerto de 91,4\%. Para a avaliação dos algoritmos, utilizamos uma metodologia que divide os dados dos questionários pelo iGovTI entre questões que serão utilizadas para aprendizado do algoritmo e questões que serão utilizadas para comparativo de predições. Para treinar o algoritmo utilizou-se 90\% dos dados e os 10\% restantes foram utilizados para avaliar a eficiência de classificação dos algoritmos, comparando a taxa de acerto entre as predições feitas e os valores reais de classificações de organizações pelo iGovTI.

Uma vez identificado um algoritmo capaz de efetuar a classificação desejada, o próximo passo é identificar as variáveis mais relevantes para esta classificação. Para isso, será utilizado o algoritmo ERV.

A ERV pode usar vários algoritmos de classificação como critério de seleção das variáveis mais importantes, escolhemos o algoritmo SVC por ele ter apresentado maior acurácia entre os algoritmos de classificação avaliados. Ainda é necessário definir o quantitativo de variáveis mais importantes a serem selecionadas. A partir da pesquisa de identificação por meio de entrevistas na APF, identificou-se 54 variáveis consideradas FCS, este critério foi utilizado para determinar o quantitativo de variáveis mais importantes para a classificação.

Assim, aplicaram-se o algoritmo ERV utilizando o SVC como critério para a seleção das variáveis mais importantes para a classificação, selecionando as 54 variáveis que correspondem aos FCS levantados nas entrevistas com os executivos de TI. Os resultados mostraram que 69,9\% das variáveis foram classificadas da mesma forma que os FCS identificados anteriormente (Quadro 10) por meio de pesquisa qualitativa.

@@

pca make possible visual discriminative analysis of reduced dataset but it is not easy make correlation betwee extracted features and its original, therefore it is necessary adictional techniques to identify CSF.

SVM have been shown to generalize well even for small sample classification[8]. SVM presents high performance to reproduce the iGovTI classification and can be used for RFE in order to identify CSF

The selected features revealed by RFE are quite similar to the qualitative analysis of Ramos \emph{et al} \cite{ramos2016information}.

### 2017-10-21 docs/thesis/chapters/6_conclusion_future_work/conclusion.tex
compiling version with all chapters
minor

\begin{enumerate}
	\item We proposed \textbf{an approach to implements DPI algorithms through MapReduce}, using whole blocks as input for Map functions. It was \textbf{shown the effectiveness of MapReduce for a DPI algorithm} to extract indicators from a distributed application traffic, also it was \textbf{shown the completion time scalability of MapReduce for DPI}, using virtual machines of a cloud provider;
	\item We developed \textit{JNetPCAP-JXTA} \citep{jnetpcapjxta}, an open source \textbf{parser to extract JXTA messages from network traffic traces};
	\item We developed \textit{Hadoop-Analyzer} \citep{Hadoopanalyzer}, an open source \textbf{tool to extract indicators from Hadoop logs and generate graphs} of specified metrics.
	\item We \textbf{characterized the behavior followed by MapReduce phases for packet level analysis and DPI}, showing that this kind of job is intense in Map phase and highlighting points that can be improved;
	\item We \textbf{described the processing capacity scalability of MapReduce for packet level analysis and DPI}, evaluating the \textbf{impact caused by variations in input size, cluster size and block size};
	\item We \textbf{showed the speed-up obtained with MapReduce for DPI}, with variations in input size, cluster size and block size;
	\item We \textbf{published two papers} reporting our results, as follows:
	\begin{enumerate}
		\item Vieira, T., Soares, P., Machado, M., Assad, R., and Garcia, V. \textit{Evaluating Performance of Distributed Systems with MapReduce and Network Traffic Analysis}. In ICSEA 2012, The Seventh International Conference on Software Engineering Advances. Xpert Publishing Services.
		\item Vieira, T., Soares, P., Machado, M., Assad, R., and Garcia, V. \textit{Measuring Distributed Applications Through MapReduce and Traffic Analysis}. In Parallel and Distributed Systems (ICPADS), 2012 IEEE 18th International Conference on, pages 704 - 705.	
	\end{enumerate}
\end{enumerate}

\subsection{Lessons Learned}
\label{sc:chaptersummary}

The contributions cited are of scientific and academic scope, with implementations and evaluations little explored in the literature. However, with the development of this work, some important lessons were learned.

During this research, different approaches for evaluating distributed systems of cloud computing providers were studied. In this period, we could see the importance of the performance evaluation in a cloud computing environment, and the recent efforts to diagnose and evaluate system at production environment of a data center. Also, the growth of the Internet and resource utilization make necessary solutions to be able to evaluate large amounts of data in short time, with low performance degradation of the evaluated system.

MapReduce has grown as a general purpose solution for big data processing, but it is not a solution for all kind of problems, and its performance is dependent of several parameters. Some researches has been done in order to improve MapReduce performance, through analytical modelling, simulation and measurement, but the most relevant contributions in this direction was guided by realistic workload evaluations, from large MapReduce clusters.

We learned that although the facilities provided by the MapReduce for distributed processing, its performance is influenced by the environment, network topology, workload, data type and by several specific parameter configurations. Therefore, an evaluation of the MapReduce behavior using data of a realistic environment will provide more accurate and wide results, while in controlled experiments the results are more restricted and limited to the evaluated metrics and factors.

@@

Because of time constraints imposed on the master degree, this dissertation addresses some problems, but some problems are still open and others are emerging from current results. Thus, the following issues should be investigated as future work:

\begin{itemize}
	\item \textbf{Evaluating of all components of the proposed approach}. This dissertation evaluated the \textit{JNetPCAP-JXTA}, the \textit{AppAnalyzer} and its implementation to evaluate a JXTA-based distributed application, it is necessary to evaluate the \textit{SnifferServer}, \textit{Manager} and the whole system working together, analysing their impact into the measured distributed system and the scalability achieved;	
	\item Development of a \textbf{technique for the efficient evaluation of distributed systems through information extracted from network traffic}. This dissertation addressed the problem of processing capacity for measuring distributed systems through network traffic analysis, but it is necessary an efficient approach to diagnose problems of distributed systems, using information of flows, connections, throughput and response time obtained from network traffic analysis;
	\item Development of a \textbf{analytic model and simulations}, using information of MapReduce behavior for network traffic analysis, measured by this dissertation, to reproduce its characteristics and enable the evaluation and prediction of some cases of MapReduce for network traffic analysis;
\end{itemize}

>>>>

\begin{enumerate}
	\item We proposed \textbf{an approach to implements DPI algorithms through MapReduce}, using whole blocks as input for Map functions. It was \textbf{shown the effectiveness of MapReduce for a DPI algorithm} to extract indicators from a distributed application traffic, also it was \textbf{shown the completion time scalability of MapReduce for DPI}, using virtual machines of a cloud provider;
	\item We developed \textit{JNetPCAP-JXTA} \citep{jnetpcapjxta}, an open source \textbf{parser to extract JXTA messages from network traffic traces};
	\item We developed \textit{Hadoop-Analyzer} \citep{Hadoopanalyzer}, an open source \textbf{tool to extract indicators from Hadoop logs and generate graphs} of specified metrics.
	\item We \textbf{characterized the behavior followed by MapReduce phases for packet level analysis and DPI}, showing that this kind of job is intense in Map phase and highlighting points that can be improved;
	\item We \textbf{described the processing capacity scalability of MapReduce for packet level analysis and DPI}, evaluating the \textbf{impact caused by variations in input size, cluster size and block size};
	\item We \textbf{showed the speed-up obtained with MapReduce for DPI}, with variations in input size, cluster size and block size;
	\item We \textbf{published five papers} reporting our results, as follows:
	\begin{enumerate}
		\item T. P. B. Vieira, D. F. Ten\'orio, J. P. C. L. da Costa, E. P. de Freitas, G. Del Galdo, and R. T. de Sousa J\'unior, \textit{Model Order Selection and Eigen Similarity based Framework for Detection and Identication of Network Attacks}. Journal of Networking and Computer Applications (JNCA), Vol 90, Jul 2017, Pages 26–41.
		\item T. Galibus, T. P. B. Vieira, E. P. de Freitas, R. Albuquerque, J. P. C. L. da Costa, R. T. de Sousa Jr, V. Krasnoproshin, A. Zaleski, H. Vissia, and G. del Galdo, \textit{Offline Mode for Corporate Mobile Client Security Architecture}. Mobile Networks and Applications, Springer, Mar 2017, Pages 1-17.
		\item K. H. C. Ramos, R. T. Sousa Jr, T. P. B. Vieira, and J. P. C. L. da Costa, \textit{DISCOVERING CRITICAL SUCCESS FACTORS FOR INFORMATION TECHNOLOGIES GOVERNANCE THROUGH BIBLIOMETRIC ANALYSIS OF RESEARCH PUBLICATIONS IN THIS DOMAIN}. Information (Yamaguchi), 2016
		\item K. H. C. Ramos, R. T. de Sousa Jr., T. P. B. Vieira, and J. P. C. L. da Costa, \textit{Identifying relevant IT governance critical success factors by means of bibliometric analysis}. 7th International Conference on Information, November 2015, Taipei, Taiwan.
		\item K. H. C. Ramos, T. P. B. Vieira, J. P. C. L. da Costa, and R. T. Sousa Jr., \textit{ANÁLISE MULTIDIMENSIONAL DE FATORES CRÍTICOS DE SUCESSO EM GOVERNANÇA DE TI NA ADMINISTRAÇÃO PÚBLICA FEDERAL À LUZ DOS DADOS DE CONTROLE EXTERNO}. in Proc. 12th International Conference on Management of Technology and Information Systems (CONTECSI), 2015, São Paulo, Brazil.
	\end{enumerate}
\end{enumerate}

@@

Because of time constraints imposed on the Ph.D. degree, this thesis addresses some problems, but some problems are still open and others are emerging from current results. Thus, the following issues should be investigated as future work:

\begin{itemize}
	\item ...;
	\item ....
\end{itemize}
